---
title:    "`r params$qaqc_params$report_title`"
subtitle: "`r params$qaqc_params$report_subtitle`"
author:   "`r params$qaqc_params$report_author`"
date:     "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    df_print: paged
    theme: cosmo
    highlight: tango
    code_folding: hide
params:
  qaqc_params: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.pos = "H",
  out.extra = ""
)

pacman::p_load(
  dplyr, tidyr, readr, stringr, forcats,
  ggplot2, scales, patchwork,
  knitr, kableExtra,
  survey, Hmisc, glue, data.table
)

p <- params$qaqc_params  # shorthand

# ── Helpers ───────────────────────────────────────────────────────────────────
#' Styled kable table for HTML
qaqc_table <- function(df, caption = "", digits = 1, ...) {
  kable(df,
    caption  = caption,
    digits   = digits,
    format   = "html",
    ...
  ) |>
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed", "responsive"),
      full_width = FALSE,
      font_size = 13
    )
}

# #' Styled kable table for PDF
# qaqc_table <- function(df, caption = "", digits = 1, ...) {
#   kable(df,
#     caption  = caption,
#     booktabs = TRUE,
#     digits   = digits,
#     linesep  = "",
#     format   = "latex",
#     ...
#   ) |>
#     kable_styling(
#       latex_options = c("HOLD_position", "striped", "scale_down"),
#       stripe_color  = "lightgray",
#       font_size     = 9
#     )
# }

#' Consistent ggplot theme
theme_qaqc <- function() {
  theme_minimal(base_size = 10) +
    theme(
      plot.title       = element_text(size = 11, face = "bold", color = "#1F618D"),
      plot.subtitle    = element_text(size = 9,  color = "grey40"),
      axis.text        = element_text(size = 8),
      axis.title       = element_text(size = 9),
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(color = "grey92"),
      legend.position  = "bottom",
      legend.text      = element_text(size = 8),
      strip.text       = element_text(size = 9, face = "bold")
    )
}

# ── Survey design (built once, reused everywhere) ─────────────────────────────
#
# All weighted estimates (means, proportions, quantiles) go through this
# svydesign object so that clustering and stratification are always accounted
# for consistently.
#
# Build is deferred to after data load (see load-data chunk).
# Access via: svy_design (global, available in all subsequent chunks)

build_svy_design <- function(df, p) {
  svydesign(
    ids     = if (!is.null(p$cluster_var) && p$cluster_var %in% names(df))
                as.formula(paste0("~", p$cluster_var)) else ~1,
    strata  = if (!is.null(p$strata_var) && p$strata_var %in% names(df))
                as.formula(paste0("~", p$strata_var)) else NULL,
    weights = as.formula(paste0("~", p$weight_var)),
    data    = df,
    nest    = TRUE
  )
}

# ── Weighted summary statistics for a numeric variable ────────────────────────

#' Compute weighted descriptive stats for one numeric variable.
#' Uses svydesign for mean/SE; weighted quantiles via Hmisc::wtd.quantile.
#' Returns a tidy data.frame(Statistic, Value).
wtd_stats <- function(svy, var, weight_var) {

  df_v <- svy$variables
  x    <- df_v[[var]]
  w    <- df_v[[weight_var]]

  # Restrict to non-missing
  ok   <- !is.na(x) & !is.na(w) & w > 0
  x_ok <- x[ok]
  w_ok <- w[ok]

  # Effective sample size (Kish formula)
  n_eff <- round(sum(w_ok)^2 / sum(w_ok^2))

  # Weighted mean & SE via survey package
  svy_sub  <- subset(svy, !is.na(svy$variables[[var]]))
  est_mean <- svymean(as.formula(paste0("~", var)), svy_sub, na.rm = TRUE)
  w_mean   <- coef(est_mean)[1]
  w_se     <- SE(est_mean)[1]

  # Weighted variance & SD
  est_var  <- svyvar(as.formula(paste0("~", var)), svy_sub, na.rm = TRUE)
  w_sd     <- sqrt(as.numeric(est_var)[1])

  # Weighted quantiles (Harrell-Davis via Hmisc, falls back to simple if absent)
  wtd_q <- tryCatch({
    Hmisc::wtd.quantile(x_ok, weights = w_ok,
                        probs = c(0, 0.25, 0.5, 0.75, 1))
  }, error = function(e) {
    # Simple weighted quantile fallback
    ord  <- order(x_ok)
    cw   <- cumsum(w_ok[ord]) / sum(w_ok)
    sapply(c(0, 0.25, 0.5, 0.75, 1),
           function(q) x_ok[ord][which(cw >= q)[1]])
  })

  # Weighted skewness: sum(w*(x - xbar)^3) / (sum(w) * sd^3)
  xbar   <- w_mean
  m3     <- sum(w_ok * (x_ok - xbar)^3) / sum(w_ok)
  w_skew <- m3 / w_sd^3

  data.frame(
    Statistic = c("N (non-missing)", "N (missing)",
                  "Effective N (Kish)", "Sum of weights",
                  "Weighted mean", "Weighted SE (mean)",
                  "Weighted std dev",
                  "Min", "Wtd P25", "Wtd median",
                  "Wtd P75", "Max",
                  "Weighted skewness"),
    Value = c(
      format(sum(ok),        big.mark = ","),
      format(sum(!ok),       big.mark = ","),
      format(n_eff,          big.mark = ","),
      format(round(sum(w_ok)), big.mark = ","),
      round(w_mean,  2),
      round(w_se,    4),
      round(w_sd,    2),
      round(wtd_q[1], 2),
      round(wtd_q[2], 2),
      round(wtd_q[3], 2),
      round(wtd_q[4], 2),
      round(wtd_q[5], 2),
      round(w_skew,  3)
    )
  )
}

# ── Weighted frequency table for a categorical variable ───────────────────────

#' Compute weighted frequencies for one categorical variable.
#' Returns a tidy data.frame(Category, N_wtd, Pct_wtd, Cum_pct).
wtd_freq <- function(svy, var, weight_var) {

  df_v <- svy$variables |> filter(!is.na(.data[[var]]))

  df_v |>
    group_by(.data[[var]]) |>
    summarise(N_wtd = sum(.data[[weight_var]]), .groups = "drop") |>
    arrange(desc(N_wtd)) |>
    mutate(
      Pct_wtd = round(N_wtd / sum(N_wtd) * 100, 1),
      Cum_pct = cumsum(Pct_wtd),
      N_wtd   = round(N_wtd)
    ) |>
    rename(Category = 1)
}

# ── Weighted proportion with CI ───────────────────────────────────────────────

#' Estimate a weighted proportion and its 95% CI.
#' numerator_expr and denom_filter are character strings evaluated on df.
#' Returns data.frame(n_wtd, pct, ci_low, ci_high).
weighted_prop <- function(df, numerator_expr, denom_filter, p) {

  df_d <- df |> filter(eval(parse(text = denom_filter)))
  if (nrow(df_d) == 0)
    return(data.frame(n_wtd = 0, pct = NA, ci_low = NA, ci_high = NA))

  svy_d <- build_svy_design(df_d, p)
  svy_d$variables$.ind <- as.numeric(
    eval(parse(text = numerator_expr), envir = svy_d$variables)
  )

  est <- svymean(~.ind, svy_d, na.rm = TRUE)
  ci  <- confint(est, level = 0.95)

  data.frame(
    n_wtd   = round(sum(df_d[[p$weight_var]], na.rm = TRUE)),
    pct     = coef(est)[1] * 100,
    ci_low  = ci[1] * 100,
    ci_high = ci[2] * 100
  )
}

#' Breakdown of weighted_prop by a grouping variable.
weighted_prop_by <- function(df, numerator_expr, denom_filter, p, by_var) {

  df |>
    filter(eval(parse(text = denom_filter)), !is.na(.data[[by_var]])) |>
    group_by(.data[[by_var]]) |>
    group_map(~ {
      res <- tryCatch(
        weighted_prop(.x, numerator_expr, "TRUE", p),
        error = function(e)
          data.frame(n_wtd = nrow(.x), pct = NA, ci_low = NA, ci_high = NA)
      )
      res[[by_var]] <- .y[[by_var]]
      res
    }) |>
    bind_rows() |>
    relocate(all_of(by_var))
}
```

```{r load-data}
df <- read_csv(p$input_file, show_col_types = FALSE)

n_rows <- nrow(df)
n_cols <- ncol(df)
n_hh   <- n_distinct(df$hhid)

# Build survey design once — reused by all weighted estimates
svy_design <- build_svy_design(df, p)
```

\newpage

# Dataset overview

```{r overview-table}
# Weighted urban/rural split
milieu_wtd <- df |>
  group_by(milieu) |>
  summarise(w = sum(.data[[p$weight_var]], na.rm = TRUE), .groups = "drop") |>
  mutate(pct = round(w / sum(w) * 100, 1))
milieu_str <- paste0(milieu_wtd$pct, "% ", milieu_wtd$milieu, collapse = " / ")

overview <- data.frame(
  Metric = c("Total individuals", "Total households",
             "Columns", "Survey waves",
             "Regions", "Urban / Rural split (weighted)"),
  Value = c(
    format(n_rows, big.mark = ","),
    format(n_hh,   big.mark = ","),
    n_cols,
    paste(sort(unique(df$vague)), collapse = ", "),
    n_distinct(df$region),
    milieu_str
  )
)

qaqc_table(overview, caption = "Dataset summary")
```

\newpage

# Data quality

## Missing values

```{r missing-values}
na_df <- df |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "N_missing") |>
  mutate(
    Pct_missing = round(N_missing / n_rows * 100, 1),
    Status = case_when(
      Pct_missing == 0            ~ "Complete",
      Pct_missing < 10            ~ "< 10%",
      Pct_missing < 50            ~ "10 – 50%",
      TRUE                        ~ "> 50%"
    )
  ) |>
  filter(N_missing > 0) |>
  arrange(desc(Pct_missing))

qaqc_table(na_df,
  caption = "Missing values by variable (only variables with at least one NA shown)",
  col.names = c("Variable", "N missing", "% missing", "Status")
)
```

```{r missing-plot, fig.cap="Missing value rate by variable (top 20)"}
na_plot <- na_df |> slice_head(n = 20) |>
  mutate(Variable = fct_reorder(Variable, Pct_missing))

ggplot(na_plot, aes(x = Pct_missing, y = Variable, fill = Status)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = paste0(Pct_missing, "%")),
            hjust = -0.1, size = 2.8) +
  scale_fill_manual(values = c(
    "Complete" = "#27AE60",
    "< 10%"    = "#F39C12",
    "10 – 50%" = "#E67E22",
    "> 50%"    = "#C0392B"
  )) +
  scale_x_continuous(limits = c(0, 110), labels = label_percent(scale = 1)) +
  labs(x = "Missing (%)", y = NULL, fill = NULL,
       title = "Missing value rate — top 20 variables") +
  theme_qaqc()
```

## Consistency checks

```{r consistency-checks}
checks_df <- purrr::map_dfr(p$consistency_checks, function(chk) {
  n_issues <- tryCatch(
    sum(eval(parse(text = chk$condition_expr), envir = df), na.rm = TRUE),
    error = function(e) NA_integer_
  )
  data.frame(
    Check    = chk$label,
    N_issues = n_issues,
    Pct      = round(n_issues / n_rows * 100, 3),
    Status   = ifelse(is.na(n_issues), "Error", ifelse(n_issues == 0, "OK", "Issues found"))
  )
})

qaqc_table(checks_df,
  caption = "Consistency checks",
  col.names = c("Check", "N issues", "% of rows", "Status")
)
```

\newpage

# Univariate analysis

## Numerical variables

```{r numeric-univariate, results='asis'}
for (v in intersect(p$vars_numeric, names(df))) {

  if (all(is.na(df[[v]]))) next

  cat(glue("\n\n### {v}\n\n"))

  # Weighted summary stats via svydesign
  stats <- wtd_stats(svy_design, v, p$weight_var)
  print(qaqc_table(stats, caption = glue("Weighted summary statistics — {v}")))

  # Weighted histogram: use weights as frequency
  df_v <- df |> filter(!is.na(.data[[v]]), !is.na(.data[[p$weight_var]]))

  p_hist <- ggplot(df_v, aes(x = .data[[v]], weight = .data[[p$weight_var]])) +
    geom_histogram(fill = "#2E86C1", color = "white", bins = 40, alpha = 0.85) +
    scale_x_continuous(labels = label_comma()) +
    scale_y_continuous(labels = label_comma()) +
    labs(x = v, y = "Weighted count",
         title    = glue("Weighted distribution — {v}"),
         subtitle = glue("Weights: {p$weight_var}")) +
    theme_qaqc()

  # Weighted boxplot by milieu (if available)
  if ("milieu" %in% names(df)) {
    df_vm <- df_v |> filter(!is.na(milieu))
    p_box <- ggplot(df_vm,
                    aes(x = milieu, y = .data[[v]],
                        weight = .data[[p$weight_var]], fill = milieu)) +
      geom_boxplot(alpha = 0.7, outlier.size = 0.8,
                   outlier.color = "#C0392B") +
      scale_y_continuous(labels = label_comma()) +
      scale_fill_manual(
        values = c("Urbain" = "#2E86C1", "Rural" = "#28B463"),
        guide  = "none"
      ) +
      labs(x = NULL, y = v, title = "By milieu") +
      theme_qaqc()
  } else {
    p_box <- ggplot(df_v, aes(y = .data[[v]],
                               weight = .data[[p$weight_var]])) +
      geom_boxplot(fill = "#2E86C1", alpha = 0.7,
                   outlier.size = 0.8, outlier.color = "#C0392B") +
      scale_y_continuous(labels = label_comma()) +
      labs(y = v, title = "Boxplot") +
      theme_qaqc() +
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
  }

  print(p_hist + p_box + plot_layout(widths = c(2, 1)))
  cat("\n\n")
}
```

## Categorical variables

```{r categ-univariate, results='asis'}
for (v in intersect(p$vars_categ, names(df))) {

  if (all(is.na(df[[v]]))) next

  cat(glue("\n\n### {v}\n\n"))

  # Weighted frequency table
  tab <- wtd_freq(svy_design, v, p$weight_var)

  print(qaqc_table(tab,
    caption   = glue("Weighted frequency table — {v}"),
    col.names = c(v, "Weighted N", "Wtd %", "Cumul. %")
  ))

  # Weighted bar chart
  n_cats <- nrow(tab)
  tab_plot <- if (n_cats > 15) slice_head(tab, n = 15) else tab
  subtitle  <- if (n_cats > 15) "(Top 15 shown)" else glue("Weights: {p$weight_var}")

  p_bar <- ggplot(tab_plot,
                  aes(x = fct_reorder(Category, Pct_wtd), y = Pct_wtd)) +
    geom_col(fill = "#2E86C1", alpha = 0.85, width = 0.7) +
    geom_text(aes(label = paste0(Pct_wtd, "%")),
              hjust = -0.1, size = 2.8) +
    coord_flip() +
    scale_y_continuous(
      limits = c(0, max(tab_plot$Pct_wtd) * 1.18),
      labels = label_percent(scale = 1)
    ) +
    labs(x = NULL, y = "Weighted %",
         title    = glue("Weighted distribution — {v}"),
         subtitle = subtitle) +
    theme_qaqc()

  print(p_bar)
  cat("\n\n")
}
```

\newpage

# Key EHCVM indicators

```{r indicators, results='asis'}
for (ind in p$indicators) {

  cat(glue("\n\n## {ind$label}\n\n"))

  # --- Overall weighted estimate ---
  overall <- tryCatch(
    weighted_prop(df, ind$numerator_expr, ind$denominator_filter, p),
    error = function(e) data.frame(n_wtd = NA, pct = NA, ci_low = NA, ci_high = NA)
  )

  overall_tab <- data.frame(
    Level    = "Overall",
    N_wtd    = format(overall$n_wtd, big.mark = ","),
    Rate_pct = round(overall$pct, 1),
    CI_95    = glue("[{round(overall$ci_low,1)}, {round(overall$ci_high,1)}]")
  )

  print(qaqc_table(overall_tab,
    caption   = glue("Overall weighted estimate — {ind$label}"),
    col.names = c("Level", "Weighted N (denom.)", "Rate (%)", "95% CI")
  ))

  # --- Breakdown by each variable ---
  plots_list <- list()

  for (by_var in intersect(ind$breakdown_vars, names(df))) {

    breakdown <- tryCatch(
      weighted_prop_by(df, ind$numerator_expr, ind$denominator_filter,
                       p, by_var),
      error = function(e) NULL
    )

    if (is.null(breakdown) || all(is.na(breakdown$pct))) next

    print(qaqc_table(
      breakdown |>
        mutate(CI_95 = glue("[{round(ci_low,1)}, {round(ci_high,1)}]")) |>
        select(-ci_low, -ci_high),
      caption   = glue("{ind$label} — by {by_var}"),
      col.names = c(by_var, "Weighted N", "Rate (%)", "95% CI")
    ))

    p_plot <- ggplot(breakdown,
                     aes(x = fct_reorder(.data[[by_var]], pct), y = pct)) +
      geom_col(fill = "#1F618D", alpha = 0.85, width = 0.65) +
      geom_errorbar(aes(ymin = ci_low, ymax = ci_high),
                    width = 0.25, color = "#C0392B", linewidth = 0.6) +
      geom_text(aes(label = paste0(round(pct, 1), "%")),
                hjust = -0.15, size = 2.8) +
      coord_flip() +
      scale_y_continuous(
        limits = c(0, min(105, max(breakdown$pct, na.rm = TRUE) * 1.2)),
        labels = label_percent(scale = 1)
      ) +
      labs(x = NULL, y = "Weighted rate (%)",
           title    = glue("{ind$label}"),
           subtitle = glue("By {by_var} — error bars: 95% CI")) +
      theme_qaqc()

    plots_list[[by_var]] <- p_plot
  }

  if (length(plots_list) > 0) {
    pairs <- split(seq_along(plots_list),
                   ceiling(seq_along(plots_list) / 2))
    for (pair in pairs) {
      if (length(pair) == 2) {
        print(plots_list[[pair[1]]] + plots_list[[pair[2]]])
      } else {
        print(plots_list[[pair[1]]])
      }
      cat("\n\n")
    }
  }
}
```

\newpage

# Bivariate analysis

## Age pyramid

```{r age-pyramid, fig.cap="Weighted age pyramid by sex", fig.height=6}
age_pyr <- df |>
  filter(!is.na(age), !is.na(sexe), !is.na(.data[[p$weight_var]])) |>
  mutate(age_group = cut(age,
    breaks = c(0, 4, 9, 14, 19, 24, 29, 34, 39, 44, 49, 54, 59, 64, 69, 200),
    labels = c("0-4","5-9","10-14","15-19","20-24","25-29",
               "30-34","35-39","40-44","45-49","50-54",
               "55-59","60-64","65-69","70+"),
    right = TRUE, include.lowest = TRUE
  )) |>
  group_by(age_group, sexe) |>
  summarise(n_wtd = sum(.data[[p$weight_var]]), .groups = "drop") |>
  mutate(n_wtd = if_else(sexe == "Masculin", n_wtd, -n_wtd))

ggplot(age_pyr, aes(x = age_group, y = n_wtd, fill = sexe)) +
  geom_col(width = 0.85, alpha = 0.9) +
  coord_flip() +
  scale_y_continuous(labels = function(x) format(abs(x), big.mark = ",")) +
  scale_fill_manual(values = c("Masculin" = "#2E86C1", "Féminin" = "#E74C3C")) +
  labs(x = "Age group", y = glue("Weighted count ({p$weight_var})"), fill = NULL,
       title    = "Weighted age pyramid",
       subtitle = "Masculin (right) | Féminin (left)") +
  theme_qaqc()
```

## Education level by sex and milieu

```{r educ-crossplot, fig.cap="Highest education level by sex and milieu (weighted, population 15+)", fig.height=5}
educ_df <- df |>
  filter(!is.na(educ_hi), !is.na(sexe), !is.na(milieu),
         age >= 15, !is.na(.data[[p$weight_var]])) |>
  group_by(educ_hi, sexe, milieu) |>
  summarise(n_wtd = sum(.data[[p$weight_var]]), .groups = "drop") |>
  group_by(sexe, milieu) |>
  mutate(pct = n_wtd / sum(n_wtd) * 100) |>
  ungroup()

ggplot(educ_df, aes(x = fct_reorder(educ_hi, pct, sum),
                    y = pct, fill = sexe)) +
  geom_col(position = "dodge", alpha = 0.85, width = 0.7) +
  facet_wrap(~milieu) +
  coord_flip() +
  scale_fill_manual(values = c("Masculin" = "#2E86C1", "Féminin" = "#E74C3C")) +
  scale_y_continuous(labels = label_percent(scale = 1)) +
  labs(x = NULL, y = "Weighted %", fill = NULL,
       title    = "Highest education level — population 15+",
       subtitle = glue("Weighted by {p$weight_var} — by sex and milieu")) +
  theme_qaqc()
```

## Activity status by age group

```{r activ-age, fig.cap="Activity status by age group — weighted (15-64 yrs)", fig.height=5}
activ_age <- df |>
  filter(age >= 15, age <= 64, !is.na(activ7j),
         !is.na(.data[[p$weight_var]])) |>
  mutate(age_grp = cut(age,
    breaks = c(15, 24, 34, 44, 54, 64),
    labels = c("15-24", "25-34", "35-44", "45-54", "55-64"),
    include.lowest = TRUE
  )) |>
  group_by(age_grp, activ7j) |>
  summarise(n_wtd = sum(.data[[p$weight_var]]), .groups = "drop") |>
  group_by(age_grp) |>
  mutate(pct = n_wtd / sum(n_wtd) * 100) |>
  ungroup()

ggplot(activ_age, aes(x = age_grp, y = pct, fill = activ7j)) +
  geom_col(position = "stack", width = 0.7, alpha = 0.9) +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(labels = label_percent(scale = 1)) +
  labs(x = "Age group", y = "Weighted %", fill = "Activity status",
       title    = "Activity status by age group",
       subtitle = glue("Weighted by {p$weight_var} — population 15–64 years")) +
  theme_qaqc()
```

## Salary distribution by region

```{r salary-region, fig.cap="Salary distribution by region (employed, non-zero salary)", fig.height=5}
sal_df <- df |>
  filter(!is.na(salaire), salaire > 0, !is.na(region))

ggplot(sal_df, aes(x = fct_reorder(region, salaire, median),
                   y = salaire, fill = region)) +
  geom_boxplot(alpha = 0.75, outlier.size = 0.5,
               outlier.color = "grey60", show.legend = FALSE) +
  scale_y_continuous(
    trans  = "log10",
    labels = label_comma(prefix = "FCFA ")
  ) +
  coord_flip() +
  labs(x = NULL, y = "Salary (log scale)", fill = NULL,
       title    = "Salary distribution by region",
       subtitle = "Employed individuals with non-zero salary — log10 scale") +
  theme_qaqc()
```

## Household size distribution by region

```{r hh-size-region, fig.cap="Household size by region", fig.height=5}
hh_size <- df |>
  filter(!is.na(menage), !is.na(region)) |>
  distinct(hhid, .keep_all = TRUE)

ggplot(hh_size, aes(x = fct_reorder(region, menage, median),
                    y = menage, fill = region)) +
  geom_violin(alpha = 0.6, show.legend = FALSE, trim = TRUE) +
  geom_boxplot(width = 0.15, fill = "white", alpha = 0.9,
               outlier.size = 0.5, show.legend = FALSE) +
  coord_flip() +
  labs(x = NULL, y = "Household size",
       title    = "Household size by region",
       subtitle = "One observation per household") +
  theme_qaqc()
```

\newpage

# Sampling weights

```{r weights-check, fig.cap="Distribution of sampling weights"}
w <- df[[p$weight_var]]

w_stats <- data.frame(
  Statistic = c("Min", "P25", "Median", "Mean", "P75", "Max",
                "CV (std/mean)", "N zero/negative"),
  Value = c(
    round(min(w,  na.rm=TRUE), 2),
    round(quantile(w, 0.25, na.rm=TRUE), 2),
    round(median(w, na.rm=TRUE), 2),
    round(mean(w, na.rm=TRUE), 2),
    round(quantile(w, 0.75, na.rm=TRUE), 2),
    round(max(w, na.rm=TRUE), 2),
    round(sd(w, na.rm=TRUE) / mean(w, na.rm=TRUE), 3),
    sum(w <= 0, na.rm=TRUE)
  )
)

qaqc_table(w_stats, caption = glue("Sampling weight summary ({p$weight_var})"))

ggplot(df, aes(x = .data[[p$weight_var]])) +
  geom_histogram(fill = "#8E44AD", color = "white", bins = 60, alpha = 0.8) +
  scale_x_continuous(labels = label_comma()) +
  labs(x = "Weight", y = "Count",
       title    = glue("Distribution of sampling weights ({p$weight_var})"),
       subtitle = "Highly unequal weights may inflate variance estimates") +
  theme_qaqc()
```

\newpage

# Session info

```{r session-info}
data.frame(
  Item  = c("R version", "Report generated", "Input file", "N rows", "N columns"),
  Value = c(
    as.character(getRversion()),
    format(Sys.time(), "%Y-%m-%d %H:%M"),
    basename(p$input_file),
    format(n_rows, big.mark = ","),
    n_cols
  )
) |>
  qaqc_table(caption = "Session information")
```
